Manuscript 1 code

### 2024-09-13 manuscript_1_code.Rmd
added site level evenness for figure 3

filtered_cover_effects_evenness <- cover_emm %>%
  left_join(diversity_ranges_quad_evenness, by = c("habitat")) %>%
  filter(evenness >= min_evenness & evenness <= max_evenness)

@@

>>>>

filtered_cover_effects_evenness <- cover_emm_evenness %>%
  left_join(diversity_ranges_quad_evenness, by = c("habitat")) %>%
  filter(evenness >= min_evenness & evenness <= max_evenness)

@@

# Figure 3f site level evenness versus cover

```{r evenness cover model site level}
evenness_cover_mod_site <- glmmTMB(cover_trans ~ evenness*habitat + (1|site) + (1|year), family = beta_family(), data = alpha_diversity_site_macro_with_cover_evenness_mod)
summary(evenness_cover_mod_site)
hist(residuals(evenness_cover_mod_site)) # little wonky but not the worst
plot(residuals(evenness_cover_mod_site) ~ fitted(evenness_cover_mod_site))
Anova(evenness_cover_mod_site)
#                   Chisq Df Pr(>Chisq)    
# evenness         14.395  1  0.0001482 ***
# habitat          45.636  3  6.777e-10 ***
# evenness:habitat 16.126  3  0.0010687 ** 
r.squaredGLMM(evenness_cover_mod_site) # 0.166, 0.258

emtrends(evenness_cover_mod_site, pairwise ~ habitat, var = "evenness") # fringing different from backreef and outer10
```

### setup

```{r figure 3f evenness site plot setup}
diversity_ranges_site_evenness <- alpha_diversity_site_macro_with_cover_evenness_mod %>%
  group_by(habitat) %>%
  summarise(min_evenness = min(evenness),
            max_evenness = max(evenness),
            min_cover= min(cover_trans),
            max_cover = max(cover_trans))

cover_emm_evenness_site <- emmip(evenness_cover_mod_site,
                        habitat ~ evenness,
                        at = list(evenness = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_cover_effects_evenness_site <- cover_emm_evenness_site %>%
  left_join(diversity_ranges_site_evenness, by = c("habitat")) %>%
  filter(evenness >= min_evenness & evenness <= max_evenness)

alpha_diversity_site_macro_with_cover_evenness_mod$habitat <- factor(alpha_diversity_site_macro_with_cover_evenness_mod$habitat, 
                             levels = c("fringing", "backreef", "outer_10","outer_17"),
                             labels = c("Fringing", "Backreef", "Forereef 10m", "Forereef 17m"))

```{r evenness cover plot site }
(figure_3f <- 
  ggplot() +
  geom_point(data = alpha_diversity_site_macro_with_cover_evenness_mod,
             aes(x = evenness, y = cover_trans, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_cover_effects_evenness_site, aes(x = evenness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_evenness_site, aes(x = evenness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "Macroalgal evenness", title = "3f. Site Level Evenness") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
